Handbook streamFind: Backend

### 2022-11-14 README.Rmd
LFU24 - update README and small fixes

The goal of streamFind is to ...

@@

You can install the development version of streamFind like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(streamFind)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

>>>>

The streamFind package is a backend (code based) and frontend ([shiny](https://shiny.rstudio.com/) app) platform for assembly of modular workflows to support spectrometric and spectroscopic data processing. The major focus of streamFind is data processing for environmental and quality studies of the water cycle. The streamFind package aims to stimulate the use of advanced data analysis (e.g., non-target screening and statistical analysis) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functionalities (modules).

@@

For installation of the streamFind package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external functionalities are used in streamFind for various processing steps. A major dependency of streamFind is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon package combines several functionalities for basic and advanced data processing and can be used interchangeably with streamFind.

### Install dependencies

#### R and RTools

[R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) for Windows users. The `r R.version.string` can be obtained in https://cran.r-project.org/. The RTools can be downloaded in https://cran.r-project.org/bin/windows/Rtools/. Make sure to download the right version for the R version installed. Installation instructions are given in both sources.

#### patRoon

The patRoon's [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) offers detailed information on how to install the [patRoon](https://github.com/rickhelmus/patRoon) R package and the required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

### Install streamFind

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository with the following code line:

```{r install-streamfind, eval=FALSE}
remotes::install_github("ricardobachertdacunha/streamFind", dependencies = TRUE)
```

## Docker image

Not yet available.

## Back-end usage

Consult the Handbook_backend_streamFind.Rmd in the handbooks folder for detailed back-end structure and usage documentation.
